Summary of Paulist missions to Catholics and non-Catholics.

```{r}
library(ggplot2)
missions <- read.csv("paulist-summary.csv")
```

How many missions were there each year?

```{r}
ggplot(data = missions) +
  geom_line(aes(x = year_start, y = missions_total))
```

How many converts were there each year?

```{r}
ggplot(data = missions) +
  geom_line(aes(x = year_start, y = converts))
```

Now you try. How many confessions were there each year?

```{r}

```

Let's make a line plot with missions to Catholics and non-Catholics. This is a line plot with missions to Catholics? How would you add a line for non-Catholic missions?

```{r}
ggplot(data = missions) +
  geom_line(aes(x = year_start, y = missions_catholic),
            color = "green") +
  ggtitle("Number of Missions to Catholics and Non-Catholics") +
  xlab(NULL) +
  ylab("Number of Missions")
```

Let's make a more bar plot of the number of missions.

```{r}
ggplot(data = missions) +
  geom_bar(aes(x = year_start, y = missions_total),
           stat = "identity") 
```

Let's do some calculations on top of 

```{r}
ggplot(data = missions) +
  geom_line(aes(x = year_start, y = confessions / missions_total))
```
